Publication Ready

### 2023-02-11 Identical_r0/Rmarkdown/Summary/r1_Best_Subsampling_Method.Rmd
publication ready and best_subsampling updated with plots

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

@@

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

>>>>

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

@@

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

### 2023-02-11 Publication_Ready.Rmd
publication ready and best_subsampling updated with plots

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

>>>>

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}
